\documentclass[12pt]{article}

\usepackage{pdfpages}
\usepackage{natbib}
\usepackage{hyperref}

% natbib
\bibpunct{(}{)}{;}{a}{}{,}
\renewcommand{\harvardurl}[1]{\textbf{URL:} \url{#1}}

\title{Codebook for ``Prediction, Proxies, and Power''}
\author{Robert J. Carroll \and Brenton Kenkel}

\begin{document}

\maketitle

\tableofcontents


\section{Dispute Outcome Expectations (DOE) Scores}

\subsection{predict-dir-dyad.csv and predict-dyad.csv}

The files \texttt{predict-dir-dyad.csv} and \texttt{predict-dyad.csv} contain the Dispute Outcome Expectations measures whose construction is described in the article.
They contain observations on all dyad-years (directed and undirected, respectively) from 1816 to 2007, according to the Correlates of War Project's State System Membership data.

Both datasets contain the same variables:
\begin{itemize}
  \item \texttt{ccode\_a}: Correlates of War code for Country A.
  \item \texttt{ccode\_b}: Correlates of War code for Country B.
  \item \texttt{year}: Year of observation.
  \item \texttt{VictoryB}: Estimated probability of victory by Country B.
  \item \texttt{Stalemate}: Estimated probability of stalemate.
  \item \texttt{VictoryA}: Estimated probability of victory by Country A.  Always equals $1 - \mathtt{VictoryB} - \mathtt{Stalemate}$.
\end{itemize}

In the directed data, Country A is assumed to be the initiator and Country B is assumed to be the target of the hypothetical dispute for which probabilities are calculated.
In the undirected data, values represent the average of the estimates for when Country A is the initiator and when Country A is the target.


\section{Correlates of War Data}

The DOE scores are calculated using two datasets from the Correlates of War project: the Militarized Interstate Disputes data, v4.01 \citep{Palmer:2015hp} and the National Material Capabilities data, v4.0 \citep{singer1972}.

\subsection{data-mida-4.01.csv and data-midb-4.01.csv}

The file \texttt{data-mida-4.01.csv} contains the dispute-level Militarized Interstate Disputes data.
The file \texttt{data-midb-4.01.csv} contains the dispute-participant--level data.
The codebook for both files is available as part of the data archive \citep{mid_data}.

\subsection{data-nmc-4.0.csv}

The file \texttt{data-nmc-4.0.csv} contains the National Material Capabilities data.
The codebook for this file is available alongside the data archive \citep{nmc_data}.


\section{Replication of Reed et al.\ (2008)}

Replication data for \citet{reed2008war}.
Obtained from \citet{reed2008data}.

\subsection{data-reed-et-al-2008.dta}

This file contains the main replication data for Reed et al.'s analysis.

\begin{itemize}
  \item \texttt{ccode1}: Country code for State 1.
  \item \texttt{ccode2}: Country code for State 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{cwmid}: Indicator for militarized interstate dispute (1 = dispute, 0 = no dispute).
  \item \texttt{alliance}: Indicator for if the states share a defense pact, neutrality agreement, or entente pact (1 = agreement, 0 = no agreement).
  \item \texttt{demlow}: Lower of the states' Polity IV scores.
  \item \texttt{logdist}: Natural logarithm of the distance between state capitals.
  \item \texttt{peaceyrs}: Years since last dispute between the states.
  \item \texttt{\_spline1}, \texttt{\_spline2}, \texttt{\_spline3}: Cubic spline basis for years since last dispute.
  \item \texttt{twomaj}: Indicator for both states being major powers (1 = both majors, 0 = not both majors).
  \item \texttt{zqpo\_1}: Absolute difference between status quo (ordinal scale measure) and balance of power.
  \item \texttt{zqpo2\_1}: Squared difference between status quo (ordinal scale measure) and balance of power.
  \item \texttt{zqpb\_1}: Absolute difference between status quo (binary scale measure) and balance of power.
  \item \texttt{zqpb2\_1}: Squared difference between status quo (binary scale measure) and balance of power.
\end{itemize}

\subsection{data-idealpoint4600.dta}

This file contains the estimated state ideal points used by Reed et al.

\begin{itemize}
  \item \texttt{ccode1}: Country code for State 1.
  \item \texttt{ccode2}: Country code for State 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{meana}: Average of posterior distribution of ideal point for State 1.
  \item \texttt{lowa}: Lowest draw from posterior distribution of ideal point for State 1.
  \item \texttt{higha}: Highest draw from posterior distribution of ideal point for State 1.
  \item \texttt{meanb}: Average of posterior distribution of ideal point for State 2.
  \item \texttt{lowb}: Lowest draw from posterior distribution of ideal point for State 2.
  \item \texttt{highb}: Highest draw from posterior distribution of ideal point for State 2.
\end{itemize}



\section{Other Replication Studies}

% See http://best-practices.dataverse.org/data-citation/ for dataset citation



\subsection{data-arena-palmer-2009.csv}

Replication data for \citet{Arena:2009gk}.
Obtained from \citet{arena2009data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for State 1.
  \item \texttt{ccode2}: Country code for State 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{init}: Indicator for dispute initiation (1 = initiation, 0 = no initiation).
  \item \texttt{gov}: Government's position along the left-right ideological spectrum. 
  \item \texttt{d\_un}: Change in unemployment.
  \item \texttt{di\_nf}: Change in inflation.
  \item \texttt{d\_gro}: Change in growth.
  \item \texttt{du\_gov}: Interaction between \texttt{d\_un} and \texttt{gov}.
  \item \texttt{di\_gov}: Interaction between \texttt{d\_inf} and \texttt{gov}.
  \item \texttt{dg\_gov}: Interaction between \texttt{d\_gro} and \texttt{gov}.
  \item \texttt{cap\_1}: Material capabilities of the democratic state.
  \item \texttt{ipeace}: Number of peace quarters in the dyad.
\end{itemize}

\subsection{data-bennett-2006.csv}

Replication data for \citet{Bennett:2006gp}.
Obtained from \citet{bennett2006data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for State 1.
  \item \texttt{ccode2}: Country code for State 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{cwinit}: Indicator for dispute initiation (1 = initiation, 0 = no initiation).
  \item \texttt{polity21}: Democracy of initiator.
  \item \texttt{polity22}: Democracy of target.
  \item \texttt{demi1simpol}: Interaction of \texttt{polity21} and similarity.
  \item \texttt{di1di2pol}: Interaction of \texttt{polity21} and \texttt{polity22}.
  \item \texttt{d1d2isqrpol}: Square of \texttt{di1di2pol}.
  \item \texttt{cap\_1}: Capability of state 1.
  \item \texttt{cap\_2}: Capability of state 2.
  \item \texttt{lndist}: Natural log of distance between states.
  \item \texttt{anypact}: Indicator for presence of a formal alliance between the states in the dyad (1 = alliance, 0 = no alliance).
  \item \texttt{priordisputeproportion}: Prior disputes between the two states in the dyad.
  \item \texttt{parity}: Parity in terms of capabilities.
  \item \texttt{cwpcetyrs}: Peace years.
  \item \texttt{cwpceyr1}: Peace years spline 1.
  \item \texttt{cwpceyr2}: Peace years spline 2.
  \item \texttt{cwpceyr3}: Peace years spline 3.
  \item \texttt{cwongo}: Indicator for ongoing war (1 = ongoing war, 0 = no ongoing war).
\end{itemize}

\subsection{data-dreyer-2010.csv}

Replication data for \citet{Dreyer:2010cu}.
Obtained from \citet{dreyer2010data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{mid}: Indicator for militarized interstate dispute (1 = dispute, 0 = no dispute).
  \item \texttt{rap\_iss\_accum}: Count of rapid issue accumulation.
  \item \texttt{grad\_iss\_accum}: Count of gradual issue accumulation.
  \item \texttt{cap\_rat}: Capability ratio.
  \item \texttt{maj\_power}: Indicator for both states being major powers (1 = both majors, 0 = not both majors).
  \item \texttt{alliance}: Indicator for formal military alliance between states (1 = alliance, 0 = no alliance).
  \item \texttt{democ}: Indicator for democracy (1 = either country democratic, 0 = neither country democratic).
  \item \texttt{contig}: Indicator for contiguity (1 = contiguous dyad, 0 = not contiguous).
  \item \texttt{spline\_1}: Spline 1.
  \item \texttt{spline\_2}: Spline 2.
  \item \texttt{spline\_3}: Spline 3.
  \item \texttt{spline\_4}: Spline 4. 
  \item \texttt{rivdyad}: Indicator for rivalry (1 = rivalry, 0 = no rivalry).
\end{itemize}

\subsection{data-fordham-2008.csv}

Replication data for \citet{Fordham:2008gs}.
Obtained from \citet{fordham2008data}.

\begin{itemize}
  \item \texttt{ccode}: Country code.
  \item \texttt{year}: Year of observation.
  \item \texttt{atopdo}: Indicator for alliance onset (1 = new alliance, 0 = none).
  \item \texttt{lnexports1}: Log of exports in previous year.
  \item \texttt{lndistance}: Log of capital to capital distance from United States.
  \item \texttt{lntotmids10\_1}:  Log of MIDs in which the United States was involved in the preceding 10 years.
  \item \texttt{lntotmids10\_2}: Log of MIDs in which other dyad member was involved in the preceding 10 years.
  \item \texttt{lndyadmid10}: Log of MIDs between United States and other dyad member in the preceding 10 years.
  \item \texttt{"lncap\_1}: Log of COW capabilities index for United States.
  \item \texttt{"lncap\_2}: Log of COW capabilities index for other dyad member.
  \item \texttt{polity22}: Polity score for other dyad member.
  \item \texttt{coldwar}: Indicator for Cold War era, 1946--1989 (1 = during Cold War, 0 = not).
  \item \texttt{noallyrs}: Count of previous alliance onsets.
  \item \texttt{\_prefail}: Count of previous alliance collapses.
  \item \texttt{\_spline1}: Spline 1.
  \item \texttt{\_spline2}: Spline 2.
  \item \texttt{\_spline3}: Spline 3.
\end{itemize}

\subsection{data-fuhrmann-sechser-2014.csv}

Replication data for \citet{Fuhrmann:2014kd}.
Obtained from \citet{fuhrmann2014data}.

\begin{itemize}
  \item \texttt{state\_a}: Country code for state 1.
  \item \texttt{state\_b}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{military\_conflict}: Indicator for militarized interstate dispute initiation (1 = dispute initiation, 0 = none).
  \item \texttt{defense\_pact\_nuclear\_cow}: Indicator for state 2 having defense pact with nuclear power (1 = pact, 0 = no pact).
  \item \texttt{nuclear\_deployment}: Indicator for state 2 having a  nuclear deployment (1 = had foreign-deployed nuclear weapons, 0 = did not).
  \item \texttt{defense\_pact\_nonnuclear\_cow}: Indicator for state 2 having a defense pact with nonnuclear power (1 = pact, 0 = no pact).
  \item \texttt{us\_troops}: Number of US troops stationed in state 2.
  \item \texttt{challenger\_nuclear\_weapons}: Indicator for state 1 being a nuclear power (1 = nuclear, 0 = not).
  \item \texttt{target\_nuclear\_weapons}: Indicator for state 2 being a nuclear power (1 = nuclear, 0 = not).
  \item \texttt{contiguity}: Indicator for contiguity (1 = contiguous, 0 = not).
  \item \texttt{alliance\_with\_challenger\_cow}: Indicator for alliance in the dyad (1 = alliance, 0 = not).
  \item \texttt{foreign\_policy\_similarity}: Foreign policy similarity.
  \item \texttt{power\_ratio}: Power ratio.
  \item \texttt{challenger\_polity}: State 1 Polity score.
  \item \texttt{target\_polity}: State 2 Polity score.
  \item \texttt{polity\_interaction}: Interaction between \texttt{target\_polity} and \texttt{challenger\_polity}
  \item \texttt{time\_conflict}: Time.
  \item \texttt{time\_conflict2}: Time squared.
  \item \texttt{time\_conflict3}: Time cubed.
  \item \texttt{politically\_relevant}: Indicator for political relevance (1 = politically relevant, 0 = not).
\end{itemize}

\subsection{data-gartzke-2007.csv}

Replication data for \citet{gartzke2007}.
Obtained from \citet{gartzke2007data}.

\begin{itemize}
  \item \texttt{statea}: COW country code for State A.
  \item \texttt{stateb}: COW country code for State B.
  \item \texttt{year}: Year of observation.
  \item \texttt{maoznewl}: Indicator for Militarized Interstate Dispute occurrence (1 = dispute, 0 = not).
  \item \texttt{demlo}: Lowest Polity IV score in the dyad, scaled to 0--10.
  \item \texttt{demhi}: Highest Polity IV score in the dyad, scaled to 0--10.
  \item \texttt{deplo}: Lowest IMF index of economic openness in the dyad.
  \item \texttt{capopenl}: Lowest score of trade openness in the dyad.
  \item \texttt{rgdppclo}: Lowest GDP per capita in the dyad.
  \item \texttt{contig}: Indicator for whether the dyad is contiguous (1 = contiguous, 0 = not).
  \item \texttt{gdpcontg}: Interaction of \texttt{rgdppclo} and \texttt{contig}.
  \item \texttt{logdstab}: Natural logarithm of great circle distance between the dyad's capitals.
  \item \texttt{majpdyds}: Indicator for if either state in the dyad is a major power (1 = major power present, 0 = none).
  \item \texttt{alliesr}: Indicator for the presence of a defense pact, neutrality pact, or entente in the dyad.  
  \item \texttt{lncaprt}: Natural logarithm of capability ratio.
  \item \texttt{namerica}: Indicator for both states being in North America (1 = yes, 0 = no).
  \item \texttt{samerica}: Indicator for both states being in South America (1 = yes, 0 = no).
  \item \texttt{europe}: Indicator for both states being in Europe (1 = yes, 0 = no).
  \item \texttt{africa}: Indicator for both states being in Sub-Saharan Africa (1 = yes, 0 = no).
  \item \texttt{nafmeast}: Indicator for both states being in North Africa or the Middle East (1 = yes, 0 = no).
  \item \texttt{asia}: Indicator for both states being in Asia (1 = yes, 0 = no).
  \item \texttt{\_spline1}, \texttt{\_spline2}, \texttt{\_spline3}: Cubic spline basis for years since last dyadic dispute.
\end{itemize}

\subsection{data-huth-2012.csv}

Replication data for \citet{Huth:2012gf}.
Obtained from \citet{huth2012data}.

\begin{itemize}
  \item \texttt{cowcntry}: Country code for state 1.
  \item \texttt{opponent}: Country code for state 2.
  \item \texttt{dvsqb}: Categorical variable for decision to challenge the status quo (0 = no challenge, 1 = negotiations, 2 = use of force).
  \item \texttt{slc3b}: Indicator for state 1 having stronger legal claims to the territory under dispute (1 = yes, 0 = no).
  \item \texttt{demdum}: Indicator for state 1 democratic (1 = democratic, 0 = not democratic).
  \item \texttt{milratio}: Capability ratio.
  \item \texttt{alliance}: Indicator for presence of an alliance (1 = alliance, 0 = no alliance).
  \item \texttt{strvalue}: Indicator for strategically valuable territory (1 = strategically valuable, 0 = not).
  \item \texttt{ethvalue1}: Indicator for state 1 having ethnic ties with a population in the disputed territory (1 = ties, 0 = no ties).
  \item \texttt{endriv5b}: Indicator for an enduring rivalry (1 = rivalry, 0 = no rivalry).
  \item \texttt{sqtime1}: Number of months to event of interest.
  \item \texttt{date}: Months since 1960.
  \item \texttt{dispno2}: Unique identifier for each separate territorial dispute.
\end{itemize}

\subsection{data-jung-2014.csv}

Replication data for \citet{Jung:2014jq}.
Obtained from \citet{jung2014data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2. 
  \item \texttt{year}: Year of observation.
  \item \texttt{dyadid}: Dyad identifier.
  \item \texttt{initiate}: Indicator for initiation of interstate conflict (1 = initiation, 0 = no initiation).
  \item \texttt{dom}: Number of political unrest events.
  \item \texttt{powtg\_cinc}: Indicator for state 2 being a rising power (1 = rising power, 0 = not).
  \item \texttt{identg}: Indicator for different religious identities in the dyad (1 = different identities, 0 = not)
  \item \texttt{tertg}: Indicator for territorial claim in last 5 years (1 = claim, 0 = no claim).
  \item \texttt{hegtg}: Indicator for state 2 being a regional or local hegemon with declining power (1 = declining hegemon, 0 = not).
  \item \texttt{caprat\_1}: Capability ratio.
  \item \texttt{cowally\_1}: Indicator for presence of an alliance (1 = alliance, 0 = none).
  \item \texttt{depend1\_1}: Economic interdependence of state 1.
  \item \texttt{depend2\_1}: Economic interdependence of state 2.
  \item \texttt{jointdemo\_1}: Indicator for joint democracy (1 = both states democratic, 0 = not).
  \item \texttt{jointminor\_1}: Indicator for both states being minor powers (1 = both minor powers, 0 = not).
  \item \texttt{border}: Indicator for sharing a border (1 = shared border, 0 = not).
  \item \texttt{lndistance}: Natural log of distance between two capitals.
  \item \texttt{mid1peace}: Years since last dyadic conflict.
  \item \texttt{mid1sp1}: Spline 1.
  \item \texttt{mid1sp2}: Spline 2.
  \item \texttt{mid1sp3}: Spline 3.
\end{itemize}

\subsection{data-morrow-2007.csv}

Replication data for \citet{morrow2007}.
Obtained from \citet{morrow2007data}.

\begin{itemize}
  \sloppy
  \item \texttt{violator\_4\_ordinal\_comply}: Categorical variable for violator's noncompliance with the laws of war (0 = full compliance, 1 = high compliance, 2 = low compliance, 3 = noncompliance)
  \item \texttt{victim\_4\_ordinal\_comply}: Categorical variable for Victim's noncompliance with the laws of war (0 = full compliance, 1 = high compliance, 2 = low compliance, 3 = noncompliance).
  \item \texttt{victim\_clar\_4\_ordinal\_comply}: Clarity of victim's violations interacted with \texttt{victim\_4\_ordinal\_comply}.
  \item \texttt{joint\_ratify\_4\_ordinal\_recip}: Interaction of \texttt{joint\_ratify} and \texttt{victim\_4\_ordinal\_comply}.
  \item \texttt{joint\_ratify\_clar\_recip}: Clarity of victim's violations interacted with \texttt{joint\_ratify\_4\_ordinal\_recip}.
  \item \texttt{victim\_individual\_comply}: Individual violations interacted with \texttt{victim\_4\_ordinal\_comply}.
  \item \texttt{victim\_state\_comply}: State violations interacted with \texttt{victim\_4\_ordinal\_comply}.
  \item \texttt{joint\_ratify}: Weighted proportion of pairs of warring states that have both ratified the most recent treaty in the issue area.
  \item \texttt{violator\_ratified}: Weighted proportion of violators that have ratified the most recent treaty in the issue area.
  \item \texttt{violator\_democracy7}: Weighted proportion of violators that are democracies.
  \item \texttt{joint\_ratify\_democracy7}: Interaction of \texttt{joint\_ratify} and \texttt{violator\_democracy7}.
  \item \texttt{violator\_ratified\_democracy7}: Interaction of \texttt{violator\_ratified} and \texttt{violator\_democracy7}.
  \item \texttt{powerratio}: Capability ratio.
  \item \texttt{joint\_ratify\_power}: Interaction of \texttt{powerratio} and \texttt{joint\_ratify}.
  \item \texttt{Aerial}: Indicator for whether issue area is aerial bombing (1 = yes, 0 = no).
  \item \texttt{Armistice}: Indicator for whether issue area is armistice (1 = yes, 0 = no).
  \item \texttt{CBW}: Indicator for whether issue area is chemical and biological warfare (1 = yes, 0 = no).
  \item \texttt{Civilians}: Indicator for whether issue area is treatment of civilians (1 = yes, 0 = no).
  \item \texttt{Cultural}: Indicator for whether issue area is protection of cultural property (1 = yes, 0 = no).
  \item \texttt{HighSeas}: Indicator for whether issue area is conduct on the high seas (1 = yes, 0 = no).
  \item \texttt{POWs}: Indicator for whether issue area is prisoners of war (1 = yes, 0 = no).
  \item \texttt{violator\_initiate}: Indicator for whether violator is war initiator (1 = yes, 0 = no).
  \item \texttt{violator\_deathsper1000population}: Violator battle deaths per 1,000 population.
  \item \texttt{victim\_victor}: Indicator for whether violator lost (1 = violator lost, 0 = violator did not lose).
  \item \texttt{victim\_victor\_power}: Interaction of \texttt{victim\_victor} and \texttt{powerratio}.
  \item \texttt{data\_quality}: Quality of data on 4-point scale.
  \item \texttt{WarDeclaration}: Indicator for declaration of war (1 = yes, 0 = no).
  \item \texttt{violatorccode}: Violator country code.
  \item \texttt{victimccode}: Victim country code.
  \item \texttt{startyear}: Year of observation.
\end{itemize}

\subsection{data-owsiak-2012.csv}

Replication data for \citet{Owsiak:2012dx}.
Obtained from \citet{owsiak2012data}.

\begin{itemize}
  \item \texttt{cdyad}: Dyad code.
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2. 
  \item \texttt{year}: Year of observation.
  \item \texttt{midonset}: Indicator for militarized interstate dispute onset (1 = dispute onset, 0 = none).
  \item \texttt{settlem}: Indicator for settled borders in the dyad (1 = settled borders, 0 = not).
  \item \texttt{jtdem6}: Indicator for whether both states are democratic (1 = yes, 0 = no).
  \item \texttt{majinvolve}: Indicator for major power involvement (1 = major power involved, 0 = not).
  \item \texttt{atopally}: Indicator for whether states are allied with each other (1 = yes, 0 = no).
  \item \texttt{lncincratio}: Natural log of CINC ratio.
  \item \texttt{peaceyears}: Peace years.
  \item \texttt{\_spline1}: Spline 1.
  \item \texttt{\_spline2}: Spline 2.
  \item \texttt{\_spline3}: Spline 3.
\end{itemize}


\subsection{data-park-colaresi-2014.csv}

Replication data for \citet{Park:2014gg}.
Obtained from \citet{park2014data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2. 
  \item \texttt{year}: Year of observation.
  \item \texttt{cwmid}: Indicator for militarized interstate dispute onset (1 = dispute onset, 0 = no dispute onset).
  \item \texttt{lowdem}: Lowest Polity IV score in the dyad.
  \item \texttt{lowgdp}: Lowest GDP in the dyad.
  \item \texttt{landcontig}: Indicator for contiguity on land (1 = contiguous, 0 = not).
  \item \texttt{nlparity}: Parity of CINC scores.
  \item \texttt{beckpeace}: Peace year (Linear).
  \item \texttt{spline1}: Peace year spline 1.
  \item \texttt{spline2}: Peace year spline 2.
  \item \texttt{spline3}: Peace year spline 3.
  \item \texttt{cvwonset}: Indicator for civil war onset (1 = civil war onset, 0 = no onset).
  \item \texttt{dyaddur}: Dyad age.
  \item \texttt{samecolony}: Indicator for shared colonial history (1 = shared colonial history, 0 = none).
  \item \texttt{ethborder}: Indicator for border dividing an ethnic group (1 = divided ethnic group, 0 = none).
  \item \texttt{terrsim}: Similarity of percentages of mountainous terrain.
  \item \texttt{prev.mid.count}: Count of previous disputes.
  \item \texttt{PostColdWar}: Indicator for a post--Cold War observation (1 = post--Cold War, 0 = not).
  \item \texttt{majdyad}: Indicator for whether at least one member of the dyad is a major power (1 = yes, 0 = no).
\end{itemize}


\subsection{data-salehyan-2008-jop.csv}

Replication data for \citet{salehyan2008}.
Obtained from \citet{salehyan2008jopdata}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{cwhostd}: Indicator for militarized interstate dispute onset (1 = dispute onset, 0 = no onset).
  \item \texttt{extbase}: Indicator for whether one state in the dyad is hosting rebels from the other (1 = yes, 0 = no).
  \item \texttt{intriv}: Indicator for international rivalry (1 = rivalry, 0 = none).
  \item \texttt{lcaprat}: Logarithm of capability ratio.
  \item \texttt{defpact}: Indicator for presence of a defense pact between countries (1 = yes, 0 = no).
  \item \texttt{politylo}: Lower Polity IV score in the dyad.
  \item \texttt{peaceyears}: Peace years.
  \item \texttt{s1}: Spline 1.
  \item \texttt{s2}: Spline 2.
  \item \texttt{s3}: Spline3.
\end{itemize}


\subsection{data-salehyan-2008-ajps.csv}

Replication data for \citet{Salehyan:2008es}.
Obtained from \citet{salehyan2008ajpsdata}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{mzinit\_lead}: Indicator for a militarized interstate dispute (1 = dispute, 0 = no dispute).
  \item \texttt{logref1}: Logged refugee stock in state 1.
  \item \texttt{logref2}: Logged refugee stock from state 1.
  \item \texttt{uppcivcon1}: Indicator for civil war in state 1 (1 = civil war, 0 = none).
  \item \texttt{uppcivcon2}: Indicator for civil war in state 2 (1 = civil war, 0 = none).
  \item \texttt{dem1}: Indicator for state 1 being a democracy (1 = democratic, 0 = not).
  \item \texttt{dem2}: Indicator for state 2 being a democracy (1 = democratic, 0 = not).
  \item \texttt{trans1}: Indicator for regime instability in state 1 (1 = instability, 0 = none).
  \item \texttt{trans2}:  Indicator for regime instability in state 2 (1 = instability, 0 = none).
  \item \texttt{contig}: Indicator for contiguity (1 = contiguous, 0 = not).
  \item \texttt{colcont}: Indicator for contiguity through colonies or dependencies (1 = contiguous, 0 = not).
  \item \texttt{capshare}: State 1's share of CINC capabilities.
  \item \texttt{s\_wt\_glo}: Alliance S-score.
  \item \texttt{depend1}: State 1's trade dependency.
  \item \texttt{depend2}: State 2's trade dependency.
  \item \texttt{igos}: Count of shared IGO memberships.
  \item \texttt{lpcyrs}: Peace years.
  \item \texttt{lpcyrs1}: Peace years spline 1.
  \item \texttt{lpcyrs2}: Peace years spline 2.
  \item \texttt{lpcyrs3}: Peace years spline 3.
\end{itemize}


\subsection{data-sobek-abouharb-ingram-2006.csv}

Replication data for \citet{Sobek:2006cn}.
Obtained from \citet{sobek2006data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{cwmid}: Indicator for onset of militarized interstate dispute (1 = dispute onset, 0 = none).
  \item \texttt{demlow}: Minimum Polity IV score.
  \item \texttt{demhigh}: Maximum Polity IV score.
  \item \texttt{caprat}: Capability ratio.
  \item \texttt{ally}: Indicator for military alliance (1 = alliance, 0 = none).
  \item \texttt{disimciv}: Indicator for dissimilar civilizations (1 = dissimilar, 0 = not).
  \item \texttt{s\_un\_glo}: S-score measure of preference similarity.
  \item \texttt{pol\_rel}: Indicator for political relevance (1 = politically relevant, 0 = not).
  \item \texttt{contig}: Indicator for contiguity (1 = contiguous, 0 = not).
  \item \texttt{physintlow}: Lower value on the physical integrity index.
  \item \texttt{empinxlow}: Lower value on the empowerment rights index.
  \item \texttt{peaceyearsmid}: Peace years.
  \item \texttt{\_spline1mid}: Spline 1.
  \item \texttt{\_spline2mid}: Spline 2.
  \item \texttt{\_spline3mid}: Spline 3.
\end{itemize}

\subsection{data-uzonyi-souva-golder-2012.csv}

Replication data for \citet{Uzonyi:2012im}.
Obtained from \citet{uzonyi2012data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{cowrecipx}: Indicator for militarized interstate dispute reciprocation (1 = reciprocated, 0 = not).
  \item \texttt{acc1nomvx}: Categorical variable for state 1 audience cost capacity (0 = no capacity, 1 = low capacity, 2 = medium capacity, 3 = high capacity).
  \item \texttt{personal1w}: Indicator for state 1 personality regime (1 = personalist, 0 = not).
  \item \texttt{single1w}: Indicator for state 1 single-party regime (1 = single-party, 0 = not).
  \item \texttt{military1w}: Indicator for state 1 military regime (1 = military, 0 = not).
  \item \texttt{hybrid1w}: Indicator for state 1 hybrid regime (1 = hybrid, 0 = not).
  \item \texttt{other1w}: Indicator for state 1 other autocratic regime (1 = other autocratic, 0 = not).
  \item \texttt{dynastic1w}: Indicator for state 1 dynastic monarchy (1 = dynastic, 0 = not).
  \item \texttt{nondynastic1w}: Indicator for state 1 non-dynastic monarchy (1 = non-dynastic, 0 = not).
  \item \texttt{interregnaw}: Indicator for state 1 interregnum autocracy (1 = interregnum autocracy, 0 = not).
  \item \texttt{interregnademw}: Indicator for state 1 interregnum democracy (1 = interregnum democracy, 0 = not).
  \item \texttt{majmaj}: Indicator for state 1 major power, state 2 major power (1 = yes, 0 = no).
  \item \texttt{minmaj}: Indicator for state 1 minor power, state 2 major power (1 = yes, 0 = no).
  \item \texttt{majmin}: Indicator for state 1 major power, state 2 minor power (1 = yes, 0 = no).
  \item \texttt{powerratio}: Capability ratio.
  \item \texttt{allies}: Indicator for alliance (1 = alliance, 0 = none).
  \item \texttt{s\_wt\_glo}: S-score measure of alliance portfolio similiarity.
  \item \texttt{s\_ld\_1}: State 1's S-score with the regional leader.
  \item \texttt{s\_ld\_2}: State 2's S-score with the regional leader.
  \item \texttt{contig400}: Indicator for contiguity (1 = contiguous, 0 = not).
  \item \texttt{terr1}: Indicator for territorial dispute (1 = territorial dispute, 0 = not).
  \item \texttt{regime1}: Indicator for regime dispute (1 = regime dispute, 0 = not).
  \item \texttt{policy1}: Indicator for policy dispute (1 = policy dispute, 0 = not).
  \item \texttt{other1}: Indicator for other dispute (1 = other dispute, 0 = not).
\end{itemize}

\subsection{data-weeks-2008.csv}

Replication data for \citet{Weeks:2008cj}.
Obtained from \citet{weeks2008data}.

\begin{itemize}
  \item \texttt{ccodecow}: Country code for state 1.
  \item \texttt{ccodecow2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{regimetype1}: Categorical variable for regime type (1 = democracy, 2 = personalist, 3 = military, 4 = single-party, 5 = hybrid, 6 = dynastic monarchy, 7 = non-dynastic monarchy, 8 = autocratic interregnum, 9 = no information, 10 = other, 11 = democratic interregnum).
  \item \texttt{majpow1}: Indicator for whether state 1 is a major power (1 = yes, 0 = no).
  \item \texttt{majpow2}: Indicator for whether state 2 is a major power (1 = yes, 0 = no).
  \item \texttt{contig}: Categorical variable for contiguity (1 = land or river border, 2 = separated by less than 12 miles of water, 3 = separated by 12--24 miles of water, 4 = separated by 25--150 miles of water, 5 = separated by 151--400 miles of water, 6 = separated by more than 400 miles of water).
  \item \texttt{s\_wt\_glo}: S-score for alliance portfolio similarity.
  \item \texttt{s\_ld\_1}: Status quo evaluation of state 1.
  \item \texttt{s\_ld\_2}: Status quo evaluation of state 2.
  \item \texttt{cwhost2}: Categorical variable for level of reciprocation by state 2 (1 = no militarized action, 2 = threat to use force, 3 = display of force, 4 = use of force, 5 = war).
  \item \texttt{cap\_1}: CINC score of state 1.
  \item \texttt{cap\_2}: CINC score of state 2. 
  \item \texttt{alliance}: Categorical variable for strength of military alliance ($-$9 = missing, 1 = defense pact, 2 = neutrality pact, 3 = entente, 4 = no alliance).
  \item \texttt{cwrevt11}: Categorical variable for type of revision (0 = none, 1 = territorial, 2 = policy, 3 = government, 4 = other).
  \item \texttt{cwnumst1}: Number of states on state 1's side in dispute.
  \item \texttt{cwnumst2}: Number of states on state 2's side in dispute.
  \item \texttt{abbrev1}: Country abbreviation for state 1.
\end{itemize}


\subsection{data-weeks-2012.csv}

Replication data for \citet{Weeks:2012be}.
Obtained from \citet{weeks2012data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{mzinit}: Indicator for militarized interstate dispute initiation (1 = initiation, 0 = no initiation).
  \item \texttt{machinejlw\_1}: Indicator for state 1's regime type being a machine (1 = yes, 0 = no).
  \item \texttt{juntajlw\_1}: Indicator for state 1's regime type being a junta (1 = yes, 0 = no).
  \item \texttt{bossjlw\_1}: Indicator for state 1's regime type being a boss (1 = yes, 0 = no).
  \item \texttt{strongmanjlw\_1}: Indicator for state 1's regime type being a strongman (1 = yes, 0 = no).
  \item \texttt{allotherauts\_1}: Indicator for state 1's regime type being any other autocracy (1 = yes, 0 = no).
  \item \texttt{newregime\_1}: Indicator for state 1's regime type being a new or unstable regime (1 = yes, 0 = no).
  \item \texttt{democracy\_1}: Indicator for state 1's regime type being democratic (1 = yes, 0 = no).
  \item \texttt{democracy\_2}: Indicator for state 2's regime type being democratic (1 = yes, 0 = no).
  \item \texttt{cap\_1}: CINC score of state 1.
  \item \texttt{cap\_2}: CINC score of state 2. 
  \item \texttt{initshare}: State 1's ratio of dyadic capabilities.
  \item \texttt{dependlow}: Lower trade dependence in dyad.
  \item \texttt{majmaj}: Indicator for state 1 major power, state 2 major power (1 = yes, 0 = no).
  \item \texttt{minmaj}: Indicator for state 1 minor power, state 2 major power (1 = yes, 0 = no).
  \item \texttt{majmin}: Indicator for state 1 major power, state 2 minor power (1 = yes, 0 = no).
  \item \texttt{contigdum}: Indicator for contiguity (1 = contiguous, 0 = not).
  \item \texttt{logdist}: Logged distance between state capitals.
  \item \texttt{s\_wt\_glo}: S-score for portfolio similarity.
  \item \texttt{s\_lead\_1}: Status quo evaluation of initiator.
  \item \texttt{s\_lead\_2}: Status quo evaluation of target.
  \item \texttt{pcyrsmzinit}: Peace years linear.
  \item \texttt{pcyrsmzinits1}: Peace years spline 1.
  \item \texttt{pcyrsmzinits2}: Peace years spline 2.
  \item \texttt{pcyrsmzinits3}: Peace years spline 3.
\end{itemize}


\subsection{data-zawahri-mitchell-2011.csv}

Replication data for \citet{Zawahri:2011iy}.
Obtained from \citet{zawahri2011data}.

\begin{itemize}
  \item \texttt{ccode1}: Country code for state 1.
  \item \texttt{ccode2}: Country code for state 2.
  \item \texttt{year}: Year of observation.
  \item \texttt{dyadcode}: Dyad code.
  \item \texttt{bilattreaty}: Indicator for bilateral treaty formation (1 = treaty, 0 = no treaty).
  \item \texttt{percentarealow}: Percent lowest area in basin.
  \item \texttt{waterdependlow}: Lowest water dependence.
  \item \texttt{avgpreciplow}: Lowest average precipitation.
  \item \texttt{lowpolity}: Lowest Polity IV score.
  \item \texttt{samelegal}: Indicator for having the same legal system (1 = yes, 0 = no).
  \item \texttt{upstreampower}: Upstream state CINC score.
  \item \texttt{downstreampower}: Downstream state CINC score.
  \item \texttt{bilatbasin}: Indicator for bilateral river basin (1 = bilateral, 0 = not bilateral).
  \item \texttt{upstreamstate}: Categorical variable for which state is upstream (A = state 1, B = state 2, AB = both).
\end{itemize}


\section{YAML Metadata}

Metadata about the models used for training and about the replication studies are contained in YAML format.
These metadata were written and produced by the authors of the manuscript.

\subsection{metadata-models.yml}

Each observation is one of the component models of the super learner used to calculate the DOE scores.

\begin{itemize}
  \item \texttt{name}: Unique identifier.
  \item \texttt{method}: Descriptive name for the model.
  \item \texttt{data}: Which variables were used to train the model.
  \item \texttt{year}: Whether a time trend is included in the model.
\end{itemize}

\subsection{metadata-replications.yml}

Each observation is one of the studies reanalyzed in the replication analysis.

\begin{itemize}
  \item \texttt{name}: Unique identifier.
  \item \texttt{author}: Last names of authors.
  \item \texttt{year}: Year of publication.
  \item \texttt{journal}: Journal of publication.
  \item \texttt{citekey}: BibTeX citation key.
  \item \texttt{repeats}: Number of repetitions used in the cross-validation analysis.
  \item \texttt{method}: Statistical model used in the analysis (logit, probit, etc.).
  \item \texttt{units}: Unit of observation in the analysis.
  \item \texttt{terms\_cinc}: Which functions of CINC scores were included in the original analysis.
  \item \texttt{terms\_doe}: Which functions of DOE scores were included in the reanalysis.
  \item \texttt{dv}: Dependent variable in the analysis.
  \item \texttt{null\_hypothesis}: Main substantive null hypothesis (or hypotheses) in the analysis.
  \item \texttt{notes}: Any additional comments.
\end{itemize}


\addcontentsline{toc}{section}{References}
\bibliographystyle{apsr}
\bibliography{doe}


\end{document}

